基于卷积神经网络的视频目标跟踪算法研究

### 2021-02-01 博士/毕业论文/ucasthesis/Tex/Chap_IGCF.tex
添加部分注释掉的内容，将图表的caption改成中文

\begin{figure}
\centering
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/00893.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01107.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01108.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01564.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01664.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01939.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02078.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02285.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02497.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02589.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02700.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03000.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03327.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03482.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03733.jpg}}
    \caption{Segmentation results of InstMask on COCO2017 \cite{COCO} validation dataset.}
    \label{fig:InstMask}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/instmask1.pdf}
    \caption{Architecture of the tracking framework IGCF.}
    \label{fig:IGCF}
\end{figure*}

@@

\iffalse
\begin{algorithm}
  \caption{The IGCF tracking algorithm.} 
  \begin{algorithmic}
    \Require Image $I_t$, object position on previous frame $p_{t-1}$, scale $s_{t-1}$, filter $h_{t-1}$, channel reliability $w_{t-1}$.
    \Ensure Position $p_t$, scale $s_t$ and updated models.
  \Statex
  \LState \textbf{Localization:}
  \begin{enumerate}[leftmargin=0pt,itemindent=1.5em]
    \item $p_t$: position of the maximum in correlation between $h_{t-1}$ and image patch features $f_{t}$ extracted on position $p_{t-1}$ and weighted by the channel reliability scores $w_{t-1}$ (Eq. \ref{eq:dcf}).
    \item Estimate segmentation mask $m$ (Sect. \ref{sec:InstMask}).
    \item Correct $p_t$ using $m$ (Sect. \ref{sec:cog}).
    \item Using location $p_t$, estimate new scale $s_ t$ as in \cite{Danelljan2014AccurateSE}.
    \item Estimate detection reliability $\tilde{w}^{(det)}$  from per-channel responses using (\ref{eq:det}).
  \end{enumerate}
  \LState \textbf{Update:}
  \begin{enumerate}[leftmargin=0pt,itemindent=1.5em]
    \item Estimate a new filter $\tilde{h}$ from $m$ using (\ref{eq:h1})$\sim$(\ref{eq:h3}).
    \item Estimate learning channel reliability $\tilde{w}^{(lrn)}$ from $h$ using (\ref{eq:lrn}).
    \item Calculate channel reliability $\tilde{w}$ using (\ref{eq:c}).
    \item Update filter $h_t$ and channel reliability $w_t$ using (\ref{eq:update1}) and (\ref{eq:update2}).
  \end{enumerate}
\end{algorithmic}
\end{algorithm}
\fi

@@

\setlength\extrarowheight{1pt}
\begin{table}
\centering
\caption{Network design of InstMask.}
\begin{tabular}{|c|c|c|}
\hline
Layers & Output Size & Support \\\hline
Data & $160 \times 160 \times 3$ &  -\\\hline
\multirow{2}*{Stem Block} & $80 \times 80 \times 64$ &  $ 7 \times 7 \text{ conv} $\\\cline{2-3}
~ & $40 \times 40 \times 64$ &  $ 2 \times 2 \text{ maxpool} $\\\hline
Res Block (1) & $40 \times 40 \times 256$ &  $ \left [ \begin{array}{l} 1 \times 1 \text{ conv} \\ 3 \times 3 \text{ conv} \\ 1 \times 1 \text{ conv} \end{array} \right ] \times 3 $\\\hline
Res Block (2) & $20 \times 20 \times 512$ &  $ \left [ \begin{array}{l} 1 \times 1 \text{ conv} \\ 3 \times 3 \text{ conv} \\ 1 \times 1 \text{ conv} \end{array} \right ] \times 4 $\\\hline
Res Block (3) & $10 \times 10 \times 1024$ &  $ \left [ \begin{array}{l} 1 \times 1 \text{ conv} \\ 3 \times 3 \text{ conv} \\ 1 \times 1 \text{ conv} \end{array} \right ] \times 6 $\\\hline
\multirow{5}*{Decoder} & $10 \times 10 \times 128$ &  $ 1 \times 1 \text{ conv} $\\\cline{2-3}
~ & $1 \times 1 \times 512$ &  $ 10 \times 10 \text{ conv} $\\\cline{2-3}
~ & $1 \times 1 \times 3136$ &  $ 1 \times 1 \text{ conv} $\\\cline{2-3}
~ & $56 \times 56$ & reshape \\\cline{2-3}
~ & $160 \times 160$ & upscale \\\hline
\end{tabular}
\label{tab:InstMask}
\end{table}

\begin{figure*}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/net.pdf}
    \caption{Architecture of our InstMask.}
    \label{fig:net}
\end{figure*}

@@

\begin{figure} 
\centering
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00003.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00005.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00007.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00013.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00057.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00002.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00005.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00011.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00013.jpg}}                     \hspace{-0.6em}    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00016.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00015.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00019.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00025.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00027.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00031.jpg}}
    \caption{The tracking result before (green) and after (blue) the instance guided self-correction component.}
    \label{fig:IGSC}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/vot/eao_rank_vot2015.png}
    \caption{Expected average overlap (EAO) plot on VOT2015 \cite{Kristan2015TheVO}.}
    \label{fig:vot15}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/vot/eao_rank_vot2016.png}
    \caption{Expected average overlap (EAO) plot on VOT2016 \cite{Kristan2016TheVO}.}
    \label{fig:vot16}
\end{figure}

@@

\section{Conclusion}
在本文中，我们提出了一种新颖的跟踪器，该跟踪器结合了深度神经网络和相关过滤器的优点来提高对象跟踪的性能。
InstMask用于约束相关滤波器的学习过程。基于实例级别的分割，我们进一步提出了一种自校正机制，以减轻对相关滤波器的漂移。
通过与最新的跟踪器进行比较，实验结果显示了该方法的出色鲁棒性和效率。

>>>>

\begin{figure}
\centering
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/00893.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01107.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01108.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01564.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01664.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01939.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02078.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02285.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02497.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02589.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02700.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03000.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03327.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03482.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03733.jpg}}
    \caption{InstMask 在 COCO2017 \cite{COCO} 验证集上的分割结果。}
    \label{fig:InstMask}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/instmask1.pdf}
    \caption{跟踪框架 IGCF 的结构。}
    \label{fig:IGCF}
\end{figure*}

@@

\begin{algorithm}
  \caption{The IGCF tracking algorithm.} 
  \begin{algorithmic}
    \Require Image $I_t$, object position on previous frame $p_{t-1}$, scale $s_{t-1}$, filter $h_{t-1}$, channel reliability $w_{t-1}$.
    \Ensure Position $p_t$, scale $s_t$ and updated models.
  \Statex
  \State \textbf{Localization:}
  \begin{enumerate}[leftmargin=0pt,itemindent=1.5em]
    \item $p_t$: position of the maximum in correlation between $h_{t-1}$ and image patch features $f_{t}$ extracted on position $p_{t-1}$ and weighted by the channel reliability scores $w_{t-1}$ (Eq. \ref{eq:dcf}).
    \item Estimate segmentation mask $m$ (Sect. \ref{sec:InstMask}).
    \item Correct $p_t$ using $m$ (Sect. \ref{sec:cog}).
    \item Using location $p_t$, estimate new scale $s_ t$ as in \cite{Danelljan2014AccurateSE}.
    \item Estimate detection reliability $\tilde{w}^{(det)}$  from per-channel responses using (\ref{eq:det}).
  \end{enumerate}
  \State \textbf{Update:}
  \begin{enumerate}[leftmargin=0pt,itemindent=1.5em]
    \item Estimate a new filter $\tilde{h}$ from $m$ using (\ref{eq:h1})$\sim$(\ref{eq:h3}).
    \item Estimate learning channel reliability $\tilde{w}^{(lrn)}$ from $h$ using (\ref{eq:lrn}).
    \item Calculate channel reliability $\tilde{w}$ using (\ref{eq:c}).
    \item Update filter $h_t$ and channel reliability $w_t$ using (\ref{eq:update1}) and (\ref{eq:update2}).
  \end{enumerate}
\end{algorithmic}
\end{algorithm}

@@

\setlength\extrarowheight{1pt}
\begin{table}
\centering
\caption{InstMask 的网络结构设计。}
\begin{tabular}{|c|c|c|}
\hline
Layers & Output Size & Support \\\hline
Data & $160 \times 160 \times 3$ &  -\\\hline
\multirow{2}*{Stem Block} & $80 \times 80 \times 64$ &  $ 7 \times 7 \text{ conv} $\\\cline{2-3}
~ & $40 \times 40 \times 64$ &  $ 2 \times 2 \text{ maxpool} $\\\hline
Res Block (1) & $40 \times 40 \times 256$ &  $ \left [ \begin{array}{l} 1 \times 1 \text{ conv} \\ 3 \times 3 \text{ conv} \\ 1 \times 1 \text{ conv} \end{array} \right ] \times 3 $\\\hline
Res Block (2) & $20 \times 20 \times 512$ &  $ \left [ \begin{array}{l} 1 \times 1 \text{ conv} \\ 3 \times 3 \text{ conv} \\ 1 \times 1 \text{ conv} \end{array} \right ] \times 4 $\\\hline
Res Block (3) & $10 \times 10 \times 1024$ &  $ \left [ \begin{array}{l} 1 \times 1 \text{ conv} \\ 3 \times 3 \text{ conv} \\ 1 \times 1 \text{ conv} \end{array} \right ] \times 6 $\\\hline
\multirow{5}*{Decoder} & $10 \times 10 \times 128$ &  $ 1 \times 1 \text{ conv} $\\\cline{2-3}
~ & $1 \times 1 \times 512$ &  $ 10 \times 10 \text{ conv} $\\\cline{2-3}
~ & $1 \times 1 \times 3136$ &  $ 1 \times 1 \text{ conv} $\\\cline{2-3}
~ & $56 \times 56$ & reshape \\\cline{2-3}
~ & $160 \times 160$ & upscale \\\hline
\end{tabular}
\label{tab:InstMask}
\end{table}

\begin{figure*}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/net.pdf}
    \caption{InstMask 的网络结构。}
    \label{fig:net}
\end{figure*}

@@

\begin{figure} 
\centering
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00003.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00005.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00007.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00013.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00057.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00002.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00005.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00011.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00013.jpg}}                     \hspace{-0.6em}    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00016.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00015.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00019.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00025.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00027.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00031.jpg}}
    \caption{实例指导（自我校正）组件之前（绿色）和之后（蓝色）的跟踪结果。}
    \label{fig:IGSC}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/vot/eao_rank_vot2015.png}
    \caption{VOT2015的预期平均重叠（EAO）图 \cite{Kristan2015TheVO}.}
    \label{fig:vot15}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/vot/eao_rank_vot2016.png}
    \caption{VOT2016的预期平均重叠（EAO）图 \cite{Kristan2016TheVO}.}
    \label{fig:vot16}
\end{figure}

@@

\section{结论}
在本文中，我们提出了一种新颖的跟踪器，该跟踪器结合了深度神经网络和相关过滤器的优点来提高对象跟踪的性能。
InstMask用于约束相关滤波器的学习过程。基于实例级别的分割，我们进一步提出了一种自校正机制，以减轻对相关滤波器的漂移。
通过与最新的跟踪器进行比较，实验结果显示了该方法的出色鲁棒性和效率。

### 2021-02-01 博士/毕业论文/ucasthesis/Tex/Chap_end.tex
添加算法
添加部分注释掉的内容，将图表的caption改成中文

\section{简介}
\label{sec:intro}
视觉对象跟踪是估计视频序列每一帧中任意目标状态的任务。 
%Recently, siamese network [] is introduced into visual tracking community, which has already been applied in many applications [].
%The key idea of siamese tracking architecture is, the target and the search image share the same feature extractor, then use correlation to tell the target position.
最近，暹罗网络已经证明了对象跟踪性能的显着提高。
%However, sometimes the performance is bad 
但是，由于视频（图\ref{fig:visulization})中的对象外观变差，例如运动模糊，遮挡等，
因此学习到的通用表示可能没有那么大的判别力。
研究人员尝试了不同的方法来改进特征表示。
例如，
%RASNet \cite{wang2018learning} explores diverse attention mechanisms to adapt the offline learned feature representations to a specific tracking target.
SA-Siam \cite{he2018twofold} 分别训练两个分支，以保持语义/外观特征的异构性。
在 DaSiamRPN \cite{zhu2018distractor}中，设计了一个新颖的可感知干扰物的增量学习模块，该模块可以有效地将常规嵌入转移到当前视频域，并在推理过程中增量捕获目标外观变化。
SiamRPN++ \cite{SiamRPN++} 引入了一种简单而有效的采样策略，以更强大的深度架构来驱动暹罗跟踪器。
这些努力产生了一些影响，并提高了最新的准确性。
%These improvements are useful.
%However, all these effort ignores a important problem: they ignore to merge the inter-frame feature during the training phase.
%One important solution is use the temporal information.
%The use of temporal information is important because, when one frame is bad, the adjusting frame can be used. While several method trying to use the temporal information, the method is naive.
%(The bug is, I cannot find any temporal information used in siamese trackers. (I cannot believe it!!! Check it again.--Checked)) For example, A use a time memory to store the appearance information. B use a simple feature average during test. C use history positional information to predict the object position in current frame. However, all these method cannot handle the temporal information during training, which lead to sub-optimal result. To solve this problem, 
但是，上述所有暹罗算法都基于仅从当前帧裁剪的特征执行跟踪，这限制了暹罗跟踪器的功能。

@@

\iffalse
Our contributions are three folds:
(1) We introduce a novel siamese tracking architecture equipped with a temporal aggregation module, which improves the per-frame features by aggregating features of adjacent frames.
(2) We incorporate the adversarial dropout module in our tracker to improve the discrimination power of the siamese tracking network.
(3) Experiments on GOT-10k and UAV20L tracking datasets show that the proposed method performs favorably against existing state-of-the-art methods (Fig. \ref{fig:visulization}).
\fi
\iffalse
\begin{itemize}
    \item We introduce a novel siamese tracking architecture equipped with a temporal aggregation module, which improves the per-frame features by aggregating features of adjacent frames.
    \item We utilize the adversarial dropout module to improve the discrimination power of the siamese tracking network.
    \item Experiments on GOT-10k and UAV20L tracking datasets show that the proposed method performs favorably against existing state-of-the-art methods.
\end{itemize}
\fi

@@

\iffalse
\begin{figure}[t]
    \centering
    \includegraphics[width=0.45\textwidth]{images/success_plot.png}
    \caption{Overall performance on GOT-10k, ranked by their average overlap (AO) scores.}
    \label{fig:got10k}
\end{figure}
\fi
\begin{table}
\centering
\caption{Performance of our algorithm with different components on GOT-10k test set.}
\begin{tabular}{c c c c c}
\bottomrule
\begin{tabular}[x]{@{}c@{}}Temporal\\aggregation\end{tabular} & \begin{tabular}[x]{@{}c@{}}Adversarial\\dropout\end{tabular} & $AO$ & $SR_{0.50}$ & $SR_{0.75}$ \\ 
\hline
          &           & 0.542 & 0.607 & 0.456 \\
\checkmark&           & 0.561 & 0.645 & 0.480 \\
\checkmark&\checkmark & 0.577 & 0.662 & 0.509 \\
\bottomrule
\label{tabel:ablation}
\end{tabular}
\end{table}
\begin{table}
\centering
\caption{将我们的方法的结果与GOT-10k测试集上的其他方法进行比较。}
\begin{tabular}{l l l l}
\bottomrule
Method   &  $AO$   &  $SR_{0.50}$ & $SR_{0.75}$  \\
\hline
Ours &  $\textbf{0.577}^\textbf{1}$ & $\textbf{0.662}^\textbf{1}$  & $\textbf{0.509}^\textbf{1}$  \\
SiamMask &  0.459&  0.560 &0.205 \\
SiamFCv2 &  0.374&  0.404 &0.144 \\
SiamFC   &  0.348&  0.353 &0.098 \\
GOTURN	 &  0.347&  0.375 &0.124 \\
CCOT	 &  0.325&  0.328 &0.107 \\
ECO	     &  0.316&  0.309 &0.111 \\
CF2	     &  0.315&  0.297 &0.088 \\
MDNet	 &  0.299&  0.303 &0.099 \\
%CFNetc2	 &  0.293&  0.265 &0.087 \\
%ECOhc	 &  0.286&  0.276 &0.096 \\
\bottomrule
\end{tabular}
\label{table:got}
\end{table}
在本小节中，我们在GOT-10k \cite{GOT-10k} 数据集上评估我们的方法。
% Say something about this dataset.
GOT-10k是最新的大规模高多样性数据集，包含10,000多个视频序列，目标序列由轴对齐的边界框注释。
%Note that the classes between training and test sets are zero-overlapped. 
%This one-shot protocol avoids the evaluation bias towards familiar objects. 
GOT-10k测试装置包括180种序列，具有84种不同的对象类别和32种运动模式。作为性能指标，我们使用 \cite{GOT-10k}中提出的平均重叠（AO）分数和成功率（SR）。AO表示所有地面和估计边界框之间重叠的平均值，而SR表示重叠超过0.5 / 0.75的成功跟踪帧的百分比。

>>>>

\section{简介}
\label{sec:intro}
视觉对象跟踪是估计视频序列每一帧中任意目标状态的任务。 
%Recently, siamese network [] is introduced into visual tracking community, which has already been applied in many applications [].
%The key idea of siamese tracking architecture is, the target and the search image share the same feature extractor, then use correlation to tell the target position.
最近，暹罗网络已经证明了对象跟踪性能的显着提高。但是，由于视频（图\ref{fig:visulization}）中的对象外观变差，例如运动模糊，遮挡等，因此学习到的通用表示可能没有那么大的判别力。
研究人员尝试了不同的方法来改进特征表示。
例如，
%RASNet \cite{wang2018learning} explores diverse attention mechanisms to adapt the offline learned feature representations to a specific tracking target.
SA-Siam \cite{he2018twofold} 分别训练两个分支，以保持语义/外观特征的异构性。
在 DaSiamRPN \cite{zhu2018distractor}中，设计了一个新颖的可感知干扰物的增量学习模块，该模块可以有效地将常规嵌入转移到当前视频域，并在推理过程中增量捕获目标外观变化。
SiamRPN++ \cite{SiamRPN++} 引入了一种简单而有效的采样策略，以更强大的深度架构来驱动暹罗跟踪器。
这些努力产生了一些影响，并提高了最新的准确性。
%These improvements are useful.
%However, all these effort ignores a important problem: they ignore to merge the inter-frame feature during the training phase.
%One important solution is use the temporal information.
%The use of temporal information is important because, when one frame is bad, the adjusting frame can be used. While several method trying to use the temporal information, the method is naive.
%(The bug is, I cannot find any temporal information used in siamese trackers. (I cannot believe it!!! Check it again.--Checked)) For example, A use a time memory to store the appearance information. B use a simple feature average during test. C use history positional information to predict the object position in current frame. However, all these method cannot handle the temporal information during training, which lead to sub-optimal result. To solve this problem, 
但是，上述所有暹罗算法都基于仅从当前帧裁剪的特征执行跟踪，这限制了暹罗跟踪器的功能。

@@

我们的贡献有三方面：
\begin{itemize}
\item 我们引入了一种新颖的暹罗跟踪体系结构，该体系结构配备了时间聚合模块，该模块通过聚合相邻帧的特征来改善每帧的特征。
\item 我们在追踪器中加入了对抗性辍学模块，以提高暹罗追踪网络的辨别能力。
\item 在GOT-10k和UAV20L跟踪数据集上进行的实验表明，该方法相对于现有的最新方法具有优越的性能（图 \ref{fig:visulization}）。
\end{itemize}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=1\textwidth]{Img/end/success_plot.png}
    \caption{GOT-10k的总体性能，按其平均重叠（AO）得分进行排名。}
    \label{fig:got10k}
\end{figure}

\begin{table}
\centering
\caption{我们的算法在GOT-10k测试仪上具有不同组件的性能。}
\begin{tabular}{c c c c c}
\bottomrule
\begin{tabular}[x]{@{}c@{}}Temporal\\aggregation\end{tabular} & \begin{tabular}[x]{@{}c@{}}Adversarial\\dropout\end{tabular} & $AO$ & $SR_{0.50}$ & $SR_{0.75}$ \\ 
\hline
          &           & 0.542 & 0.607 & 0.456 \\
\checkmark&           & 0.561 & 0.645 & 0.480 \\
\checkmark&\checkmark & 0.577 & 0.662 & 0.509 \\
\bottomrule
\label{tabel:ablation}
\end{tabular}
\end{table}
\begin{table}
\centering
\caption{将我们的方法的结果与GOT-10k测试集上的其他方法进行比较。}
\begin{tabular}{l l l l}
\bottomrule
Method   &  $AO$   &  $SR_{0.50}$ & $SR_{0.75}$  \\
\hline
Ours &  $\textbf{0.577}^\textbf{1}$ & $\textbf{0.662}^\textbf{1}$  & $\textbf{0.509}^\textbf{1}$  \\
SiamMask &  0.459&  0.560 &0.205 \\
SiamFCv2 &  0.374&  0.404 &0.144 \\
SiamFC   &  0.348&  0.353 &0.098 \\
GOTURN	 &  0.347&  0.375 &0.124 \\
CCOT	 &  0.325&  0.328 &0.107 \\
ECO	     &  0.316&  0.309 &0.111 \\
CF2	     &  0.315&  0.297 &0.088 \\
MDNet	 &  0.299&  0.303 &0.099 \\
%CFNetc2	 &  0.293&  0.265 &0.087 \\
%ECOhc	 &  0.286&  0.276 &0.096 \\
\bottomrule
\end{tabular}
\label{table:got}
\end{table}
在本小节中，我们在GOT-10k \cite{GOT-10k} 数据集上评估我们的方法。
% Say something about this dataset.
GOT-10k是最新的大规模高多样性数据集，包含10,000多个视频序列，目标序列由轴对齐的边界框注释。
%Note that the classes between training and test sets are zero-overlapped. 
%This one-shot protocol avoids the evaluation bias towards familiar objects. 
GOT-10k测试装置包括180种序列，具有84种不同的对象类别和32种运动模式。作为性能指标，我们使用 \cite{GOT-10k}中提出的平均重叠（AO）分数和成功率（SR）。AO表示所有地面和估计边界框之间重叠的平均值，而SR表示重叠超过0.5 / 0.75的成功跟踪帧的百分比。

### 2021-02-01 博士/毕业论文/ucasthesis/Tex/Chap_globally.tex
添加部分注释掉的内容，将图表的caption改成中文

\iffalse
Another advantage of this globally spatial-temporal perception mechanism is that it use the RoI Align \cite{He2018MaskR} operation to enable the tracker to take advantage of deeper networks \HL{for feature learning, which is not acceptable for the popular local mechanism-based SiamFC \cite{SiamFC} and SiamRPN \cite{SiamRPN} trackers, because the padding in their network structures} will destroy the strict translation invariance \cite{SiamFC}. \HL{Specifically}, the entire template image and search image in our tracker are sent to the same backbone network to extract features,  \HL{and} then the object features are obtained \HL{using} the RoI Align operation from the template features according to the ground truth of the \HL{initial frame}. The object features and the search \HL{image} features are cross-correlated by channel to obtain \HL{a fusion feature map}, which \HL{is} sent to the subsequent tracking \HL{modules}. \HL{Since this new} solution has no restrictions on the \HL{translation invariance, we} can use the powerful ResNet \cite{he2016deep} as the backbone network \HL{to accurately model the discrimination between the foreground object and background clutters.}
\fi

\iffalse
To sum up, this paper makes following three main contributions.
(1) Based on the global perception mechanism, we introduce a two stage tracking pipeline using a very deep network to reduce cumulative inaccuracies and improve robustness.
(2) A novel unified end-to-end convolutional neural network architecture \HL{for} trajectory prediction is proposed, where historical trajectory information and appearance information of the current frame are used to predict the target position distribution.
(3) We demonstrate the effectiveness of our proposed 
Globally Spatial-Temporal Perception-based tracking system (GSTP)
\HL{by showing} that the tracking performance \HL{performs favorably against}
other state-of-the-art approaches on the \HL{GOT-10k \cite{GOT-10k} and UAV20L \cite{mueller2016benchmark} Long-term Tracking datasets}.
\fi

>>>>

这种全球时空感知机制的另一个优势是，它使用 RoI Align \cite{He2018MaskR} 操作使跟踪器能够利用更深的网络进行特征学习，这对于流行的基于本地机制的SiamFC \cite{SiamFC} 和SiamRPN \cite{SiamRPN} 跟踪器，因为其网络结构中的填充将破坏严格的转换不变性 \cite{SiamRPN++}. 具体来说，将跟踪器中的整个模板图像和搜索图像发送到相同的主干网络以提取特征，然后根据初始帧的基本情况使用RoI Align操作从模板特征中获取对象特征。通过通道使对象特征和搜索图像特征互相关以获得融合特征图，该融合特征图被发送到后续的跟踪模块。由于此新解决方案对平移不变性没有任何限制，因此我们可以使用功能强大的ResNet \cite{he2016deep} 作为骨干网络来准确地建模前景对象与背景杂波之间的区别。

综上所述，本文做出以下三个主要贡献。
\begin{itemize}
\item 基于全局感知机制，我们引入了一个两步跟踪管道，该管道使用非常深的网络来减少累积误差并提高鲁棒性。
\item 提出了一种新颖的统一的端到端卷积神经网络的轨迹预测结构，利用历史轨迹信息和当前帧的出现信息来预测目标位置分布。
\item 我们在 GOT-10k \cite{GOT-10k} 和UAV20L \cite{mueller2016benchmark} 长期跟踪数据库上优秀的性能证明了我们提出的基于全球时空知觉的跟踪系统（GSTP）的有效性。
\end{itemize}
